Peer Assessment 1 (Reproducible Research)
========================================================

This is a report on 17,568 observations of steps monitoring.

## Loading and preprocessing the data

```{r, echo = TRUE }
  library(ggplot2)
  library(plyr)
  download.file('https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip', 
                'activity.zip', method="curl")
  unzip('activity.zip')
  activity <- read.csv("activity.csv", stringsAsFactors=FALSE)
  activity$date <- as.Date(activity$date, "%Y-%m-%d")  
```

## What is mean total number of steps taken per day?

```{r, echo = TRUE}
  perDay <- setNames(aggregate(activity$steps, list(activity$date), FUN = sum, na.rm = TRUE), 
                     c('date','totalSteps')) 
  ggplot(perDay, aes(x=totalSteps)) + geom_histogram()
  mean(perDay$totalSteps, na.rm=TRUE)
  median(perDay$totalSteps, na.rm=TRUE)
```

## What is the average daily activity pattern?

```{r, echo = TRUE}
  perInterval <- setNames(aggregate(activity$steps, list(activity$interval), FUN = mean, na.rm = TRUE),
                     c('interval','avgSteps'))  
  ggplot(perInterval, aes(x=interval, y=avgSteps)) + geom_line()
  subset(perInterval, subset=(avgSteps == max(perInterval$avgSteps))) 
```

## Imputing missing values
```{r, echo = TRUE}
  sum(is.na(activity$steps))
  activityFilled <- ddply(activity, "interval", function(df)
    {df$steps[is.na(df$steps)] <- mean(df$steps, na.rm=TRUE); return(df)})
  perDay <- setNames(aggregate(activityFilled$steps, list(activityFilled$date), FUN = sum, na.rm = TRUE), 
                     c('date','totalSteps')) 
  ggplot(perDay, aes(x=totalSteps)) + geom_histogram()
  mean(perDay$totalSteps, na.rm=TRUE)
  median(perDay$totalSteps, na.rm=TRUE)
  
```
By filling the missing values with the interval average, the total steps mean was significantly increased but not the median. 

## Are there differences in activity patterns between weekdays and weekends?

```{r, echo = TRUE}
activityFilled$weekD <- weekdays(activityFilled$date)
activityFilled$dayType[activityFilled$weekD %in% c("Monday","Tuesday","Wednesday","Thursday","Friday")] <- "weekday"
activityFilled$dayType[activityFilled$weekD %in% c("Saturday","Sunday")] <- "weekend"
activityFilledType <- ddply(activityFilled, c("dayType","interval"), summarize, steps = mean(steps))
```
Weekdays vs Weekends
```{r, echo = TRUE}
qplot(interval, steps, data=activityFilledType, geom="line", facets=dayType~.)
```




